Blas\'e3D

### 2023-11-07 paper/paper2/ms.tex
Pair writing: again this time

\begin{mdframed}
    \textbf{Emulation with blas\'e}

    - Per-grid point optimization procedure
    - Pretrained model caching
    - Output storage

\begin{mdframed}
    \textbf{Open Source Availability}

>>>>

\begin{mdframed}
    \textbf{Cloning with blas\'e}

    - Per-grid point optimization procedure
    - Pretrained model caching
    - Output storage
    \\---------------\\
    Blas\'e's algorithm is designed to take a spectrum as input, and outputs two products:
    1. A list of detected spectral line properties, all assumed to be Voigt profiles, and 2.
    A cloned spectrum, which is the aggregation of all of those detected lines into a spectrum. We
    don't use the cloned spectrum from this process, and only focus on the line properties that are output.
    These two products are stored as a .pt file, which can then be loaded in in order to 
    analyze all the lines in bulk. Each grid point is processed in this way, and the resulting .pt files'
    line properties are aggregated into a single DataFrame, which can then be queried by $T_eff$, $\log(g)$, $Z$,
    in addition to the actual line in question, identified by its center $\mu_j$.
\end{mdframed}

\begin{mdframed}
    \textbf{Open Source Availability}
    \\--------------\\
    The PHOENIX model grid is available open-source at $xx$, and can be interfaced with gollum,
    also available open-source at $xx$. Blas\'e is also available open-source at $xx$, with this work
    existing as a fork named blas\'e3D, available at $xx$.
\end{mdframed}
